Network Origins of Social Distinction

### 2025-07-20 manuscript.tex
do it

\subsection{Distinction Centrality's Measurement Parameters}
In Figure 1, we present a variety of toy models that compare the effects of network interconnections on the status and constraint of actors. In each model, there are seven nodes, and node 1 is the best-connected node in the network. Thus, node 1 always has an eigenvector centrality of 1. However, the distinction of node 1 changes based on the interconnection of the other nodes, demonstrating how distinction centrality captures the question of constraint exerted by neighbors.

@@

@@

\subsection{Distinction with Structural Holes vs. Structural Folds}

@@

%Placehold graphs
%\begin{figure}
%   \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
%    \centering
%     \begin{subfigure}[b]{0.45\textwidth}
%        \includegraphics[width=1.0\textwidth]{Plots/sf.png}
%            \caption{Star Graph}
%            \label{fig:Placehold}
%    \end{subfigure}
%     \begin{subfigure}[b]{0.45\textwidth}
%        \includegraphics[width=1.0\textwidth]{Plots/sf.png}
%            \caption{Structural Fold}
%            \label{fig:Placehold}
%    \end{subfigure}
%    \caption{Structural Holes with more added subgraphs.}
%    \label{fig:toys}
%\end{figure}

@@

\subsection{Long Ties and Hierarchy}
This section highlights how the hierarchy is really formed out of the redundant connections of the subgraphs. While a star graph clearly creates a hierarchy, when additional weight is added to the broker's alters, the hierarchy can be flipped, especially when they form denser subgraphs. This is in keeping with the observed structural holes above.

@@

%NOTES FROM 7|19|25 Meeting
%***Triadic closure as distinction maximization*** 
%Strogatz is random, preferential attachment of closure
%Status homophilous (enh) attachment vs preferential vs random 
%I wonder how much of balance theory is really just distinction maximization?
%Non psychological theory polarity

%Triadic closure 3 versions
%-Psychology
%-Polarity, valenced ties 
%-Status distinction

>>>>

\subsection{Distinction Centrality's Measurement Parameters}
Below, we present a variety of toy models that compare the effects of network interconnections on the status and constraint of actors.

\subsubsection{Structural Holes vs Structural Folds}
 In each model, there are seven nodes, and node 1 is the best-connected node in the network. Thus, node 1 always has an eigenvector centrality of 1. However, the distinction of node 1 changes based on the interconnection of the other nodes, demonstrating how distinction centrality captures the question of constraint exerted by neighbors.

@@

\subsubsection{Circle Graphs and Triadic Closure}
%NOTES FROM 7|19|25 Meeting
%***Triadic closure as distinction maximization*** 
%Strogatz is random, preferential attachment of closure
%Status homophilous (enh) attachment vs preferential vs random 
%I wonder how much of balance theory is really just distinction maximization?
%Non psychological theory polarity

%Triadic closure 3 versions
Psychology
Polarity, valenced ties 
Status distinction

@@

@@

@@

\subsubsection{Long Ties and Hierarchy}
This section highlights how the hierarchy is really formed out of the redundant connections of the subgraphs. While a star graph clearly creates a hierarchy, when additional weight is added to the broker's alters, the hierarchy can be flipped, especially when they form denser subgraphs. This is in keeping with the observed structural holes above.

@@
